Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-01-15 TEBenchmarkPaper/article.tex
Cite Advice Taker

A fundamental limitation of our benchmarking approach is that it only applies to
systems which act in ``batch mode'', i.e. those which choose to halt after
emitting some output. Whilst all of the systems we have encountered are of this
form, an analogous benchmark may be desirable for systems which instead run
continuously or interactively (perhaps akin to McCarthy's ``advice taker'').%FIXME~\cite{}.

>>>>

A fundamental limitation of our benchmarking approach is that it only applies to
systems which act in ``batch mode'', i.e. those which choose to halt after
emitting some output. Whilst all of the systems we have encountered are of this
form, an analogous benchmark may be desirable for systems which instead run
continuously or interactively (perhaps akin to McCarthy's
``advice taker''~\cite{McCarthy_Programs59}).
